---
title: "Final Group Project: AirBnB analytics"
date: "12 Oct 2021"
author: "Reading Time: About 8 minutes"
output:
  html_document:
    highlight: zenburn
    theme: flatly
    toc: yes
    toc_float: yes
    number_sections: yes
    code_folding: show
---


```{r setup, include=FALSE}
# leave this chunk alone
options(knitr.table.format = "html") 
knitr::opts_chunk$set(warning = FALSE, message = FALSE, 
  comment = NA, dpi = 300)
```


```{r load-libraries, echo=FALSE}
library(tidyverse) # the usual stuff: dplyr, readr, and other goodies
library(lubridate) # to handle dates
library(GGally) # for correlation-scatter plot matrix
library(ggfortify) # to produce residual diagnostic plots
library(rsample) # to split dataframe in training- & testing sets
library(janitor) # clean_names()
library(broom) # use broom:augment() to get tidy table with regression output, residuals, etc
library(huxtable) # to get summary table of all models produced
library(kableExtra) # for formatting tables
library(moderndive) # for getting regression tables
library(skimr) # for skim
library(mosaic)
library(leaflet) # for interactive HTML maps
library(tidytext)
library(viridis)
library(vroom)
```


```{r load_data, echo=FALSE, message=FALSE, warning=FALSE, cache=TRUE}

listings <- 
  vroom("http://data.insideairbnb.com/turkey/marmara/istanbul/2021-09-30/data/listings.csv.gz") %>% 
       clean_names()
```

# Exploratory Data Analysis (EDA)

##Raw Value Inspection

There are 23,019 entries and 74 characteristics for each entry. 

```{r}
glimpse(listings)
```
##Summary Statistics & Finding Missing Entries

Through skimming the data, we see that there are 23 character, 5 date, 9 logical, and 37 numeric variables. Numeric variables include but not limited to number of accommodates that a property can host, bedrooms, minimum & maximum nights for stay, review scores, and availability within upcoming days. Categoric variables include but not limited to property and room types, verification status of the host, number of bathrooms in a property, and neighborhood.  

For certain variables like bathrooms and license, all the entries are missing. Therefore, before dropping off the missing values immediately, first we need to eliminate the variables that we do not think will be useful for our analysis. Then, we can drop the missing values for the variables of interest. Additionally, some of the important variables like price is stored as a character. So, we need to convert it into numeric variable before we start building our model (see data wrangling). 

Computing the summary statistics for number of reviews, minimum/maximum nights, and availability of the property for the next 30 and 365 days, we learn about the distribution of values (min, max, Q1, Q3, median) as well as the basic explanatory statistics like mean, standard deviation, count and number of missing values. Since we base our analysis on a travel data, we should eliminate the properties that are available only for the long-term rent. When we check the explanatory statistics and the box plot for the minimum night for stay (see data wrangling), the maximum value is 730. This means, there is a property who is only available if the guest is going to stay for minimum 730 days. Therefore, we filter our dataframe according to travel conditions. 


###Finding Missing Values & Variable Types
```{r}
skimr::skim(listings)
```

###Summary Statistics for Certain Numeric Variables
```{r}
round(mosaic::favstats(unlist(listings ["number_of_reviews"])), digits=2)
```

```{r}
round(mosaic::favstats(unlist(listings ["minimum_nights"])), digits = 2)
```

```{r}
round(mosaic::favstats(unlist(listings ["maximum_nights"])), digits = 2)
```

```{r}
round(mosaic::favstats(unlist(listings ["availability_30"])), digits = 2)
```

```{r}
round(mosaic::favstats(unlist(listings ["availability_365"])), digits = 2)
```

```{r}
round(mosaic::favstats(unlist(listings ["review_scores_rating"])), digits = 2)
```

##Data Wrangling

###Changing the Types of Variables of Interest

To prepare the variables for the regression model later, we need to modify some of them and change their variable type. For example, we changed the variable types of price and host response rate from a character variable to a numeric variable for the model regression in the next part of this report. This step is necessary because both these variables are numeric variables. 

```{r}
#Change the type of Price to Numeric
listings <- listings %>% 
  mutate(price = parse_number(price))
#Change the type of Host Response Rate to Numeric
listings$host_response_rate <- round((as.numeric(gsub('.{1}$', '', 
                                  listings$host_response_rate)))/100, digits=2)
#Change the type of Bathroom to Numeric
listings$bathrooms_text <- as.numeric(sub("^(.{1}).*", "\\1",
                                          listings$bathrooms_text ) )
listings <- listings %>% 
  mutate(bathrooms=bathrooms_text ) #changed name of bathroom_text to bathrooms
listings %>% 
  select(bathrooms)
```

###Filtering & Choosing Variables of Interest & Dropping Missing Values

Most common values for minimum nights is 1. As discussed above, there are properties that are only available for the long-term rent. For example, there is a property with minimum night stay of 730 days. Since we consider travel conditions, we should eliminate those by filtering minimum_nights <= 4 below.
 
```{r}
#Box plot for Minimum Nights & Filtering for Travel Conditions
ggplot(listings, aes(y= minimum_nights)) +
  geom_boxplot()+
  theme_bw() +
  labs(title= "Box Plot for Minimum Nights",
       y="Minimum Nights") 
```
One of the more prominent factors our group thinks will affect AirBnb price is the type of property that is being leased. Therefore, we proceeded on to have a look at the various property types available in the dataset, but find that there is 94 different categories. Upon listing the weight of various property types represented in the sample, we noticed that the top 4 categories comprise 68.6% of all the property types - which is more than half. 

Therefore, to simplify the analysis, we decided to clean this variable and only include the top 4 categories of property types - which are "entire rental unit", "private room in rental unit", " room in boutique hotel", and "entire serviced apartment". The remaining property types are then summed and categorised as "others". 

``` {r}
#Defining 5 Categories for Property Type
listings %>% 
  group_by(property_type) %>% 
  summarise(count= count (property_type)) %>% 
  mutate(percentage= count/(sum(count))*100 ) %>% 
  arrange(desc(percentage))

listings <- listings %>%
  mutate(prop_type_simplified = case_when(
    property_type %in% c("Entire rental unit","Private room in rental unit", 
                         "Room in boutique hotel",
                         "Entire serviced apartment") ~ property_type, 
    TRUE ~ "Other"
  ))
listings %>%
  count(property_type, prop_type_simplified) %>%
  arrange(desc(n))  

unique(listings ["prop_type_simplified"])

```
Following property types, our group continued discussing which variables we felt mattered the most it terms of influencing AirBnb prices. We shortlisted a list of variables for further exploration, and they are explored below. 

```{r}
#Creating a new dataframe with variables of interest
new_listings<- listings %>% 
  select(price, 
         prop_type_simplified, 
         room_type, 
         neighbourhood_cleansed,
         host_response_rate, 
         accommodates, 
         bathrooms, 
         bedrooms, 
         beds, 
         minimum_nights, 
         maximum_nights, 
         availability_30,
         availability_60,
         availability_90,
         availability_365,
         number_of_reviews, 
         review_scores_rating, 
         review_scores_accuracy, 
         review_scores_cleanliness, 
         review_scores_checkin, 
         review_scores_communication, 
         review_scores_location, 
         review_scores_value, 
         instant_bookable, 
         reviews_per_month, 
         has_availability, 
         host_identity_verified, 
         host_has_profile_pic,
         host_is_superhost) %>%
  filter(accommodates >1,minimum_nights <= 4)
#Since we are interested in properties for 2 people, we need to eliminate the 
# properties for only one person
#Our analysis is based on the travel data, so we filter the entries with 
# minimum_nights <= 4
#Dropping missing values of the new dataframe
new_listings <-drop_na(new_listings)
head(new_listings)

skimr::skim(new_listings)

```

##Informative Visualization

As we see from the graph, the distribution of price is positively skewed with most of the values <1,000 and some very large values like +100,000. Computing the explanatory statistics, we see that mean price is 562.24 while the maximum price is 80,089.

```{r fig.width = 12, fig.height = 12}
#Density Plot for Price
ggplot(new_listings, aes(x= price)) +
  geom_density(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Density Plot for Price",
    y     = "Density",
    x= "Price")
ggplot(new_listings, aes(y= price)) +
  geom_boxplot() +   
  theme_bw() +                
  labs (
    title = "Box Plot for Price",
    y     = "Price")

round(mosaic::favstats(unlist(new_listings ["price"])), digits = 2)

```

Plotting the histogram for availability within x= 30, 60, 90 and 365 days, we see that in each case, most of the properties are either not available or available +(x-5) days. Exceptionally, in the case of availability within the next 365, there is a seasonal pattern in every 100 days. So, some of the properties are available within next 100 days, 200 days, or +300 days. 

```{r fig.width = 12, fig.height = 12}
#Histogram for Availability within next 30 days 
ggplot(new_listings, aes(x= availability_30)) +
  geom_histogram(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Histogram for Availability Within Next 30 Days",
    x= "Availability within next 30 days",
    y= "Number of Properties")
```

```{r fig.width = 12, fig.height = 12}
#Histogram for Availability within next 60 days 
ggplot(new_listings, aes(x= availability_60)) +
  geom_histogram(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Histogram for Availability Within Next 60 Days",
    x= "Availability within next 60 days",
    y= "Number of Properties")
```

```{r fig.width = 12, fig.height = 12}
#Histogram for Availability within next 90 days 
ggplot(new_listings, aes(x= availability_90)) +
  geom_histogram(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Histogram for Availability Within Next 90 Days",
    x= "Availability within next 90 days",
    y= "Number of Properties")
```

```{r fig.width = 12, fig.height = 12}
#Histogram for Availability within next 365 days 
ggplot(new_listings, aes(x= availability_365)) +
  geom_histogram(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Histogram for Availability Within Next 365 Days",
    x= "Availability within next 365 days",
    y= "Number of Properties")
```
Since we filtered data based on travel conditions (minimum_nights<=4), we have 4 values for this variable; 1, 2, 3 and 4. Majority of the properties have a minimum 1-night stay. This is followed by properties having a minimum stay of 2, 3, then 4 nights. 

```{r fig.width = 12, fig.height = 12}
#Histogram for Minimum Nights 
ggplot(new_listings, aes(x= minimum_nights)) +
  geom_histogram(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Histogram for Minimum Nights",
    x= "Minimum Nights",
    y= "Number of Properties")
```
Since reviews left by previous customers can be an important source of informaiton for potential customers interested in the apartment, we decided to further explore this variable as well.

A density plot is made for the number of reviews left for each property. On average, guests make around 10 reviews per property. However, there are some properties with significant number of reviews (e.g., 606). Considering the density plot for number of reviews, data is positively skewed with majority of data points being around 0 to 100 reviews per property. 

```{r fig.width = 12, fig.height = 12}
#Density plot for Number of Reviews 
ggplot(new_listings, aes(x= number_of_reviews)) +
  geom_density(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Density Plot for Number of Reviews",
    y     = "Density",
    x="Number of Reviews")

round(mosaic::favstats(unlist(new_listings ["number_of_reviews"])), digits = 2)

```
Then, we followed to create another density plot, which shows the distribution of review scores for the apartments. 

Majority of the reviews are centered around 5 with a mean 4.57 and median 4.8. We can assume that, guests provide rating when they are satisfied with the property/host/service, etc. If they think that the service is on average or below average, they do not provide as much as feedback as they do when they are satisfied. 

We would expect higher concentration around rating= 1 & 2, because people tend to give feedback when they are not satisfied with the service they get. However, alternatively, there might not be much dissatisfaction and guests are happy with the service they get. 

```{r fig.width = 12, fig.height = 12}
#Density Plot for Review Scores Rating
ggplot(new_listings, aes(x= review_scores_rating)) +
  geom_density(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Density Plot for Review Scores Rating",
    y     = "Density",
    x= "Review Scores Rating")

round(mosaic::favstats(unlist(new_listings ["review_scores_rating"])), 
      digits = 2)

```
Size of an apartment can also influence its price significantly. For example, we expect a property that can accommodate more people to be larger, and therefore influence its price as well. A histogram is used to explore the distribution of people that a property is able to accommodate across the dataset. 

We also mutated the variable, and converted the count of property types accommodating different number of people into a percentage of the entire dataset. 37% of properties listed accommodate 2 people. The percentage properties with +6 accommodates is very low approximately 6%. 

```{r fig.width = 12, fig.height = 12}
#Histogram for Number of Accommodates
ggplot(new_listings, aes(x= accommodates )) +
  geom_histogram(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Number of Accommodates in a Property",
    x= "Accomodates",
    y= "Number of Properties")
new_listings %>% 
  group_by(accommodates) %>% 
  summarise(count=count(accommodates)) %>% 
  mutate(percentage= count/sum(count) *100) %>% 
  arrange(desc(percentage))
```
There are 5 property types (simplified version). Within those 5 units, "Entire Rental Unit" has the majority of the weight, 48.5% followed by "Other" 25.43%.

We created a bar chart below, to show the number of properties in each category type. We also mutated the variable, to calculate the percentage of each type of property type. We wanted to see the composition of property types across the dataset. The table below summarizes the percentage and count of each property type, and is arranged in descending order. 

```{r fig.width = 12, fig.height = 12}
#Bar chart for Property Type
ggplot(new_listings, aes(y= prop_type_simplified )) +
  geom_bar(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Property Type",
    x="Number of Properties",
    y="Property Type")
new_listings %>% 
  group_by(prop_type_simplified) %>% 
  summarise(count=count(prop_type_simplified)) %>% 
  mutate(percentage= count/sum(count) *100) %>% 
  arrange(desc(percentage))
```
Another variable of interest is the types of rooms available.There are 4 types of rooms, "Entire home", "Private room", "Hotel room", and "Shared room".We expect rooms that have more privacy to be priced more expensive than those which have to be shared. To prepare this variable for use in our model regression later, we created a bar plot, to give a good visual representation of the number of listings in each category. From the barplot, it is obvious that most of the listed properties are entire home. This is then followed by private room, hotel room, and shared home. 

We also mutated the count of listed properties into a percentage. Approximately 70% of listings are in the "entire home/apt" category. 

```{r fig.width = 12, fig.height = 12}
#Bar chart for Room Type
ggplot(new_listings, aes(y= room_type )) +
  geom_bar(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Room Type",
    x= "Number of Properties",
    y= "Room Type")
new_listings %>% 
  group_by(room_type) %>% 
  summarise(count=count(room_type)) %>% 
  mutate(percentage= count/sum(count) *100) %>% 
  arrange(desc(percentage))
```

The next variable to be explored is neighborhood. Depending on how touristic, posh, or convenient the neighborhood is, the price of listings may also change. To prepare this variable for later use in our model, we prepared a barplot to give a visual breakdown of neighborhood types represented in the dataset. From the chart, a huge majority of the properties are in Beyoglu & Fatih which are the most touristic regions of Istanbul. 

```{r fig.width = 12, fig.height = 12}
#Bar chart for Neighborhood
ggplot(new_listings, aes(y= neighbourhood_cleansed )) +
  geom_bar(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Neighborhood",
    x= "Number of Properties",
    y= "Neighborhood")
```
Convenience in booking should also be an important factor influencing prices of listing. If the listing can be easily booked, then it saves a lot of time and brings convenience to users. Therefore, we expect that if a listing can be instantly booked, then the price should also take this convenience into account. 

We plotted a bar chart to see the number of instantly and non-instantly bookable units. There are approximately 4000 instant bookable properties and 3000 not instantly bookable ones. 
```{r fig.width = 12, fig.height = 12}
#Bar chart for Instant Bookable
ggplot(new_listings, aes(x= instant_bookable)) +
  geom_bar(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Instant Bookability",
    x= "Status of Instant Bookability",
    y= "Number of Properties")
new_listings %>% 
  count(instant_bookable) 
```

Identity verification might be a significant factor in determining the price of a property. If the host identity is verified, potential customers may feel "safer" to book the listing with a peace of mind that their host is verified by a third-party and not likely to be a scam. We made a barplot and also table, to show the number of verified hosts - which is nearly 83% of the dataset. 

```{r fig.width = 12, fig.height = 12}
#Bar chart for Host Identity Verification
ggplot(new_listings, aes(x= host_identity_verified  )) +
  geom_bar(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Host Identity Verification",
    y= "Number of Identifications",
    x= "Identity Verification Status")
new_listings %>% 
  count(host_identity_verified) 
```
Does each scatterplot support a linear relationship between variables? Do any of the correlations appear to be conditional on the value of a categorical variable?

##Correlations

Computing the correlation between the numeric variables, we see that review scores are strongly positively correlated with each other. For example, the correlation between review_scores_accuracy and review_scores_rating is 0,875 and the correlation between review_scores_communication and review_scores_cleanliness is 0,833. To prevent collinearity, we should not include all review scores in our regression models, but rather just include review_scores_rating.

Moreover, the correlation between the availability of 30, 60, 90, and 365 days is high, so similar exclusion to prevent collinearity holds for these variables. For example, the correlation between the availability within 60 and 30 days is 0,917 which is almost 1. 

Interestingly, we see that the number of reviews has relatively low correlation with other numeric variables whşch is around 10% (except number of reviews per month).

The strongest correlation with price is number of accommodates which is 0,244.

```{r fig.width = 20, fig.height = 20}
correlation_data <- new_listings %>% 
  dplyr::select(where(is.numeric)) %>% 
  ggpairs()
correlation_data
```
# Mapping 

Visualisations of feature distributions and their relations are key to understanding a data set, and they can open up new lines of exploration. While we do not have time to go into all the wonderful geospatial visualisations one can do with R, you can use the following code to start with a map of your city, and overlay all AirBnB coordinates to get an overview of the spatial distribution of AirBnB rentals. For this visualisation we use the `leaflet` package, which includes a variety of tools for interactive maps, so you can easily zoom in-out, click on a point to get the actual AirBnB listing for that specific point, etc.

The following code, having downloaded a dataframe `listings` with all AirbnB listings in Milan, will plot on the map all AirBnBs where `minimum_nights` is less than equal to four (4). You could learn more about `leaflet`, by following [the relevant Datacamp course on mapping with leaflet](https://www.datacamp.com/courses/interactive-maps-with-leaflet-in-r)

The below map gives an overview of the spatial distribution of AirBnb in Istanbul, with minimum nights less than 4. 

```{r, out.width = '80%'}
leaflet(data = filter(listings, minimum_nights <= 4)) %>% 
  addProviderTiles("OpenStreetMap.Mapnik") %>% 
  addCircleMarkers(lng = ~longitude, 
                   lat = ~latitude, 
                   radius = 1, 
                   fillColor = "blue", 
                   fillOpacity = 0.4, 
                   popup = ~listing_url,
                   label = ~property_type)
```



    
# Regression Analysis

For the target variable $Y$, we will use the cost for two people to stay at an Airbnb location for four (4) nights. 

Create a new variable called `price_4_nights` that uses `price`, and `accomodates` to calculate the total cost for two people to stay at the Airbnb property for 4 nights. This is the variable $Y$ we want to explain.



```{r}
four_nights_for_two_listings <- new_listings %>%
  filter(minimum_nights <= 4 & maximum_nights >= 4 & accommodates >= 2) %>% 
  mutate(price_4_nights = price * 4) # Total cost of staying four nights 
skim(four_nights_for_two_listings)
```

Use histograms or density plots to examine the distributions of `price_4_nights` and `log(price_4_nights)`. Which variable should you use for the regression model? Why?
```{r}
#Density Plot for price_4_nights
ggplot(four_nights_for_two_listings, aes(x= price_4_nights)) +
  geom_density(alpha=0.2) +   
  theme_bw() +                
  labs (
    title = "Density Plot for price_4_nights",
    y     = "Density",
    x= "price_4_nights")
```
```{r}
#Density Plot for log(price_4_nights)
ggplot(four_nights_for_two_listings, aes(x= price_4_nights)) +
  geom_density(alpha=0.2) +   
  scale_x_log10() +
  theme_bw() +                
  labs (
    title = "Density Plot for log(price_4_nights)",
    y     = "Density",
    x= "log(price_4_nights)")
```


Fit a regression model called `model1` with the following explanatory variables: `prop_type_simplified`, `number_of_reviews`, and `review_scores_rating`. 
```{r}
model1 <- lm(log(price_4_nights) ~ prop_type_simplified + number_of_reviews + 
               review_scores_rating, data = four_nights_for_two_listings)
 
mosaic::msummary(model1)
```


- Interpret the coefficient `review_scores_rating` in terms of `price_4_nights`.
- Interpret the coefficient of `prop_type_simplified` in terms of `price_4_nights`.

We want to determine if `room_type` is a significant predictor of the cost for 4 nights, given everything else in the model. Fit a regression model called model2 that includes all of the explananatory variables in `model1` plus `room_type`. 
```{r}
model2 <- lm(log(price_4_nights) ~ prop_type_simplified + number_of_reviews + 
               review_scores_rating + room_type, 
             data = four_nights_for_two_listings)

mosaic::msummary(model2)
```

## Further variables/questions to explore on our own

Our dataset has many more variables, so here are some ideas on how you can extend your analysis

1. Are the number of `bathrooms`, `bedrooms`, `beds`, or size of the house (`accomodates`) significant predictors of `price_4_nights`? Or might these be co-linear variables?

```{r}
#Test whether these variables are significant predictors of 'price_4_nights'

model_test<- lm(log(price_4_nights) ~ bathrooms + bedrooms + beds + 
                  accommodates, data = four_nights_for_two_listings)

mosaic::msummary(model_test)

```

```{r}
#Create a new column named log_price
four_nights_for_two_listings <- four_nights_for_two_listings %>% 
  mutate(log_price = log(price_4_nights))

#Check whether they are co-linear variables 
correlation_check <- four_nights_for_two_listings %>% 
  select(log_price, bathrooms, bedrooms, beds, accommodates)%>% 
  ggpairs()
  
correlation_check
```


1. Do superhosts `(host_is_superhost`) command a pricing premium, after controlling for other variables?


1. Some hosts allow you to immediately book their listing (`instant_bookable == TRUE`), while a non-trivial proportion don't. After controlling for other variables, is `instant_bookable` a significant predictor of `price_4_nights`?


1. For all cities, there are 3 variables that relate to neighbourhoods: `neighbourhood`, `neighbourhood_cleansed`, and `neighbourhood_group_cleansed`. There are typically more than 20 neighbourhoods in each city, and it wouldn't make sense to include them all in your model. Use your city knowledge, or ask someone with city knowledge, and see whether you can group neighbourhoods together so the majority of listings falls in fewer (5-6 max) geographical areas. You would thus need to create a new categorical variabale `neighbourhood_simplified` and determine whether location is a predictor of `price_4_nights`

```{r}
#Group neighbourhood into 6 areas based on their geographical position
unique(four_nights_for_two_listings$neighbourhood_cleansed)

east <- c("Pendik","Tuzla","Cekmekoy","Sancaktepe","Sile","Umraniye",
          "Kartal","Maltepe")
central_west <- c("Beyoglu","Sariyer","Sisli", "Besiktas","Kagithane")
central_east <- c("Uskudar","Kadikoy","Beykoz","Adalar","Atasehir")
west_south <- c("Bagcilar","Basaksehir","Bakirkoy","Bahcelievler",
                "Zeytinburnu","Bayrampasa","Gungoren","Gaziosmanpasa",
                "Esenler")
west <- c("Esenyurt","Avcilar","Silivri","Buyukcekmece","Kucukcekmece",
          "Catalca","Beylikduzu")
west_north <- c("Arnavutkoy","Eyup","Fatih","Sultangazi")

four_nights_for_two_listings <- four_nights_for_two_listings %>% 
  mutate(neighbourhood_simplified = case_when(
    neighbourhood_cleansed %in% east ~ "East", 
    neighbourhood_cleansed %in% central_west ~ "Central_west",
    neighbourhood_cleansed %in% central_east ~ "Central_east",
    neighbourhood_cleansed %in% west_south ~ "West_south",
    neighbourhood_cleansed %in% west ~ "West",
    neighbourhood_cleansed %in% west_north ~ "West_north"
  ))


unique(new_listings$neighbourhood_simplified)

```

```{r}
model3 <- lm(log(price_4_nights) ~ prop_type_simplified + number_of_reviews + 
               review_scores_rating + instant_bookable + 
               neighbourhood_simplified, data = four_nights_for_two_listings)

mosaic::msummary(model3)
```

Adding in a model for reviews, check for correlations between reviews per month and 30 day availability first: 

```{r}
#Check whether they are co-linear variables 

correlation_check_availability_reviewspcm <- four_nights_for_two_listings %>% 
  select(log_price, availability_30, reviews_per_month)%>% 
  ggpairs()
  
correlation_check_availability_reviewspcm
```
Seem fine so adding these to a fourth model: 

```{r}
model4 <- lm(log(price_4_nights) ~ prop_type_simplified + number_of_reviews + 
               review_scores_rating + availability_30 + reviews_per_month, 
             data = four_nights_for_two_listings)

mosaic::msummary(model4)
```

Create a model5 which combines elements of 2 and 3:

```{r}
model5<- lm(log(price_4_nights) ~ prop_type_simplified + number_of_reviews + 
               review_scores_rating + neighbourhood_simplified + room_type, 
             data = four_nights_for_two_listings)

mosaic::msummary(model5)
```

## Diagnostics, collinearity, summary tables

As you keep building your models, it makes sense to:

1. Check the residuals, using `autoplot(model_x)`
```{r}
library(ggfortify)

autoplot(model1) + 
  theme_bw()

autoplot(model2) + 
  theme_bw()

autoplot(model3) + 
  theme_bw()

autoplot(model4) + 
  theme_bw()

autoplot(model5) + 
  theme_bw()

```


Having built our five models, we will use `car::vif(model_x)`` to calculate the **Variance Inflation Factor (VIF)** for our predictors and determine whether we have colinear variables. 

```{r}
# Check whether any model has a VIF (Variance Inflation Factor) greater than 5
car::vif(model1)
car::vif(model2)
car::vif(model3)
car::vif(model4)
car::vif(model5)
```



1. Create a summary table, using `huxtable` (https://mfa2022.netlify.app/example/modelling_side_by_side_tables/) that shows which models you worked on, which predictors are significant, the adjusted $R^2$, and the Residual Standard Error.


```{r}
# Compare models using 'huxtable'
huxreg(model1, model2, model3, model4, model5,
       statistics = c('#observations' = 'nobs', 
                      'R squared' = 'r.squared', 
                      'Adj. R Squared' = 'adj.r.squared', 
                      'Residual SE' = 'sigma'), 
#       bold_signif = 0.05, 
       stars = NULL
) %>% 
  set_caption('Comparison of models')
```

1. Finally, you must use the best model you came up with for prediction. Suppose you are planning to visit the city you have been assigned to over reading week, and you want to stay in an Airbnb. Find Airbnb's in your destination city that are apartments with a private room, have at least 10 reviews, and an average rating of at least 90. Use your best model to predict the total cost to stay at this Airbnb for 4 nights. Include the appropriate 95% interval with your prediction. Report the point prediction and interval in terms of `price_4_nights`. 
  - if you used a log(price_4_nights) model, make sure you anti-log to convert the value in $. You can read more about [hot to interpret a regression model when some variables are log transformed here](https://stats.idre.ucla.edu/other/mult-pkg/faq/general/faqhow-do-i-interpret-a-regression-model-when-some-variables-are-log-transformed/)

```{r}
# Filter a private room, at least 10 reviews, average rating of at least 90% of 
# 5 (since the rating is from 0 to 5, not 0 to 100)

updated_four_nights_for_two_listings <- four_nights_for_two_listings %>% 
  filter(room_type == "Private room" & number_of_reviews >= 10 & 
           review_scores_rating >= 4.5)

head(updated_four_nights_for_two_listings)

```

```{r}
# Use broom::augment(). It's  essentially the same thing as predict(), 
# but it adds the predictions and confidence intervals to the data set
model_predictions <- broom::augment(model5, 
                             newdata = updated_four_nights_for_two_listings)

# Now we have two new columns named .fitted and .se.fit: .fitted is the
# predicted value and .se.fit is the standard error of the predicted value
model_predictions

model_predictions_antilog <- model_predictions %>%
  mutate(.fitted_new = exp(.fitted))

# We can plot the neighbourhood predictions:
ggplot(model_predictions_antilog, aes(x = neighbourhood_simplified, 
                                      y = .fitted_new)) +
  geom_line() +
  labs(y = "Predicted Price for 4 Nights", # Change this to a line of best fit
       x = "Neighbourhood")+
  theme_bw() + 
  NULL

# Plotting the ratings 

ggplot(model_predictions_antilog, aes(x = review_scores_rating, 
                                      y = .fitted_new)) + 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(y = "Predicted Price for 4 Nights", x = "Rating") +
  NULL

# Plotting the number of reviews 

ggplot(model_predictions_antilog, aes(x = number_of_reviews, 
                                      y = .fitted_new)) + 
  geom_point() +
  geom_smooth(method = "lm", se = FALSE) + 
  labs(y = "Predicted Price for 4 Nights", x = "Number of Reviews") +
  NULL

```


# Conclusions

1) Maybe Istanbul is weird?
2) Other factors affecting price
3) Strong adjiusted $R^2$ in the end


# Acknowledgements

- The data for this project is from [insideairbnb.com](insideairbnb.com)
